Analysis of bulk void regions

### 2014-05-08 cosmic_voids.tex
Subsection of watershed transform over FA field for void classification

%-------------------------------------------------------------------------
\subsection{The cosmic web in Bolshoi}
\label{subsec:web_in_simulations}
%-------------------------------------------------------------------------

@@

Finally, we also calculate typical distributions of the density and 
peculiar velocity fields in each type of environment, obtaining completely
analogous results. Furthermore, we also use a BDM catalogue of the 
simulation, obtaining very similar conclusions.

@@

In the figure \ref{fig:FA_field} we calculate the FA field over the 
simulation for both web schemes. The first interesting feature of this
figure is the degeneration presented for knots and central regions of 
voids, where both of them exhibit low to middle values of the FA, 
indicating a high isotropy regarding the physical properties quantified by 
each web scheme, i.e. the density field for the T-web and the peculiar 
velocity for the V-web. For the T-web, the FA field near to knots presents 
a very narrow distribution around a local minima, whereas for the V-web 
such distribution is more spread out. This can be explained appealing to 
the low fluctuations of the density field compared with the peculiar 
velocity in highly non-linear regions like knots. For more linear regions 
like voids, the behaviour of the FA field is quite similar between both 
schemes, what is consistent with the equivalence of the T-web and the 
V-web in the linear regime \SRKED{[reference, Hoffman]}.

@@

%-------------------------------------------------------------------------
\subsection{Identifying void regions}
\label{subsec:identification}
%-------------------------------------------------------------------------

>>>>

%-------------------------------------------------------------------------
\subsection{Dark matter halos as tracers of the cosmic web}
\label{subsec:halos_cosmicweb}
%-------------------------------------------------------------------------

@@

Finally, we also calculate typical distributions of the density and 
peculiar velocity fields in each type of environment by using all cells of
the simulation grid instead of dark matter halos, obtaining completely
analogous results. Furthermore, we also use a BDM catalogue for the dark
matter halos, obtaining very similar results.

@@

In the figure \ref{fig:FA_field} we calculate the FA field over the 
simulation for both web schemes. The first interesting feature of this
figure is the degeneration presented for knots and central regions of 
voids, where both of them exhibit low to middle values of the FA, 
indicating a high isotropy regarding the physical properties quantified by 
each web scheme, i.e. the density field for the T-web and the peculiar 
velocity for the V-web. For the T-web, the FA field near to knots presents 
a very narrow distribution around a local minimum, whereas for the V-web 
such distribution is more spread out. This can be explained appealing to 
the low fluctuations of the density field compared with the peculiar 
velocity in highly non-linear regions like knots. For more linear regions 
like voids, the behaviour of the FA field is quite similar between both 
schemes, what is consistent with the equivalence of the T-web and the 
V-web in the linear regime \SRKED{[reference, Hoffman]}.

@@

%-------------------------------------------------------------------------
\subsection{Identifying void regions through web schemes}
\label{subsec:identification}
%-------------------------------------------------------------------------

Resuming our endeavour at identifying voids in cosmological simulations, 
previous techniques based on web classification schemes usually perform a 
FOF-like algorithm over cells previously marked as voids according to some 
established criteria in order to construct bulk void regions 
\SRKED{[references]}. Although this method has some success at classifying 
voids, percolation is completely inevitable, where the only way to reduce 
it is artificially decreasing the global volume fraction of void regions 
such that they do not merge significantly each other.

Once has been determined the reliability of the FA index for tracing 
different properties of voids, our novel proposal here is rather using the 
FA field for classifying void regions. As was concluded in the previous 
subsection, the geometry of voids is completely traced by contours of the
FA field, where central parts of voids and high density knot regions 
exhibit particularly low values of the FA index. Therefore, through a 
watershed transform all voids are classified, where each single void 
region corresponds to the basin of a local minimum of the FA field, where
those local minimums are restricted to be embedded into a type-void cell
in order to avoid degeneracy with knots.
